A recipe for extremely reproducible enrichment analysis

### 2023-04-13 manuscript.Rmd
Update manuscript.Rmd

| S.No.| Pubmed ID | Replication of (Table/Figure) | Replication was possible? 1. Were the terms the same as authors? 2. Were there other significant terms found which were not mentioned in the article? |	Summary | Replication Classified as 1, 2, 3 |
| --- | -------- | ---- | ---- | ---- | ---- |
| 1. | PMC6349697 | Figure 2C and 2D |	1. Yes, however, corrected p values are different after replication. 2. Yes, only BP terms were taken into account so several CC and MF significant terms were not mentioned in the paper. |	The basis of the selection of just 6 gene ontologies and 4 KEGG pathways shown in the paper needs to be addressed when there is a higher amount of significant GOs and pathways are observed after replication. It was impossible to determine if the article utilised a background gene list or not. The steps to perform DAVID analysis could have been elaborated in the paper. The results shown in the paper are observed after replication but only 6 BP GO significant terms are shown in the paper. |	3 [Considering top 6 BP Terms and KEGG pathways] |

>>>>

| S.No.| Pubmed ID | Replication of (Table/Figure) | 1. Was Replication possible? 2. Were there other significant terms found which were not mentioned in the article? |	Summary | Replication Classified as 1, 2, 3 |
| --- | --- | --- | --- | --- | --- |
| 1. | PMC6349697 | Figure 2C and 2D |	1. Yes, however, corrected p values are different after replication. 2. Yes, only BP terms were taken into account so several CC and MF significant terms were not mentioned in the paper. |	The basis of the selection of just 6 gene ontologies and 4 KEGG pathways shown in the paper needs to be addressed when there is a higher amount of significant GOs and pathways are observed after replication. It was impossible to determine if the article utilised a background gene list or not. The steps to perform DAVID analysis could have been elaborated in the paper. The results shown in the paper are observed after replication but only 6 BP GO significant terms are shown in the paper. |	3 [Considering top 6 BP Terms and KEGG pathways] |
| 2. | PMC6368841 | Figure 3 A - D |	1. Only GO Terms were the same as the paper. KEGG terms were highly inconsistent. 2. Replicated KEGG Terms (using DAVID) were not mentioned in the results of the paper. Shows inconsistency due to the usage of the server. Some terms using clusterprofiler in R were mentioned. | GO results from the original manuscript is somewhat similar to reproduced analysis. The FDR values however are inconsistent. KEGG results were highly different. The list of genes as input into DAVID analysis is unclear. They should have mentioned both up and down-regulated proteins were considered. | 2 |
| 3. | PMC6381667 | Figure 1 and Figure 2 | 1. Results are not reproducible and are highly inconsistent 2. N.A. |	1. GO terms obtained after replication showed inconsistent results compared to the results in the original article. KEGG results were similar. 2. Better naming convention for supplementary file for 117 genes for DAVID input is necessary. 3. GO Results are not reproducible and are highly inconsistent. | 2 |
| 4. | PMC6405693	| Table 1 and Table 2; Texts under “Protein-Protein Interaction Network Building and Interrelation Analysis Between Pathways”	| 1. Results do not match. 2. N.A. |	1. GO analysis from upregulated and downregulated proteins are less similar to the results given in the paper. The FDR values for some pathways are highly inconsistent. 2.KEGG Analysis of all DEGs do not match at all. |	1 |
| 5. | PMC6425008 |	Most of the tables and figures of the paper (Figure 5, 6, 7), Table 2	| 1. No. 2. N.A. |	1. This paper could have done proper labelling of supplementary files as it was difficult the gene list for DAVID analysis. 2. Lacks information on when control genes are used and when citral-affected gene lists are used. 3. Replication of GO and KEGG analysis is not consistent with results from the paper. 4. How were Figures 5-7 derived? 5. The overall protocol is not so coherent. | 1 |
| 6. | PMC6444048	| The text under “Pathway analysis of SUVmax related genes” And Table 2 |	1. Terms are the same but gene counts have been different. The DAVID results are somewhat reproducible. 2. No |	1. Gene counts in the terms significantly enriched in the “process of cell division” and “nucleoplasm” has changed. 
2. Only cell cycle is highly enriched in the replicated results, the claims of metabolic pathways and hypoxia signalling (through GSEA analysis) to be enriched are not accurate. The results claimed are somewhat similar. All the processes have different FDR values. | 3 |
| 7. | PMC6463127 |	Table 4, Table 5, Table 6	| 1. Yes but the significance differed. 2. Yes, several terms from replication were not mentioned in the paper for GO Analysis. | Does not consider corrected p values. Overall, significant terms from GO analysis of up and downregulated DEGs are missing upon replication. | 2 |
| 8. | PMC6535219 |	Figure 2 | 1. Somewhat similar. 2. There were many top significant terms that were not mentioned.	Narrowing/Filtering the given gene list is a required step that could have been mentioned. Many terms were not so significant anymore. There were new terms that are of top positions after replication. | 1 |
| 9. | PMC6539328 |	Figure 1A |	1. Mostly not. 2. Yes, many	The significant pathways stated in the paper are not showing up once replicated. There is no clarity of the up-regulated genes used for GO and KEGG analysis. Only 21 upregulated genes are listed whereas the paper states 4831. Also, why are only upregulated genes are being used? | 1 |
| 10. | PMC6542760 | Figure 4 |	1. No. 2. Yes, many significant terms were observed. | Replication results of GO terms are not at all compliant with the results shown in the paper. | 1 |
| 11. | PMC6557785 | Figure 5 A-B |	1. Yes, but results in paper are not significant upon replication. 2.  Yes | For GO terms, there are other terms that have higher numbers of genes, making them more enriched than immune-related pathways as mentioned in the paper. For KEGG Pathways, there are other pathways that are more significant and contain a higher number of genes enriched for example “Salmonella infection” that has a higher count of genes but is not mentioned in the paper. | 2 |
| 12. | PMC6561911 | Figure 5 a and b	| 1. No. 2. N.A. | The enrichment analysis results are inconsistent with the results displayed in the paper. There was no KEGG analysis done | 1 |
| 13. | PMC6580941 | Table 1 and Table 2 | 1. Yes. 2. Yes! Significant terms like “nucleoplasm”, “RNA Binding”, “protein binding” are missing from the paper. |	For GO analysis, the replicated results are not as significant as the GO terms shown in Tables 1 and 2 of the paper. The Gene list for input is not so clearly mentioned, it should have been labelled properly in the name of the supplemental file. P-values are completely different. | 2 |
| 14. | PMC6587650 | 	Figure 2 |	1. Yes. 2. Yes, som. | The GO terms results of BP, MF, CC and KEGG pathway results from the paper are compliant with replicated results. They could have mentioned why they chose the type of sorting shown in the paper to display their results. Overall, all results have been replicated.	| 3 [Best] |
| 15. | PMC6591946 | Figure 5 c and Figure 6 a |	1. Yes for GO analysis only. 2. Yes for KEGG analysis |	The GO term results of replication are compliant with Figure 5 c of the paper. KEGG pathway results are semi-consistent. | 2 |
| 16. | PMC6663624 |	Table 3 and Table 4	| 1. Yes. 2. Yes | The top 2 significant GO terms in the paper are not significant after replication analysis is done. Other GO terms are the same as replicated results. For KEGG Analysis, some terms are more significant after replication. Eg: PD-L1 expression and PD-1 checkpoint pathway in cancer, Th1 and Th2 cell differentiation, Th17 cell differentiation were more significant after “natural killer (NK) cell-mediated cytotoxicity” KEGG Pathway. The paper is somewhat replicable. | 1 |
| 17. | PMC6582306 |	Figure 5 |	1. Partly. 2. Yes, many. |	The paper uses 44 sets of DEGs grouped in 4 major types. For replication, OFC Set 9 was used, DAVID GO analysis was done twice where a discrepancy of results was observed. Compared to the paper, the most significant term was missing after replication analysis was conducted. For OFC set 9, several pathways are seen after replication but only one pathway is shown in paper. This should be addressed. |	2 |
| 18. | PMC6333352 |	Figure 7 |	1. Yes. 2. Yes. There was a difference in gene counts as well. | DAVID was used for KEGG Analysis: From WGCNA - Bahn - KEGG Analysis: Epstein-Barr virus infection, the pathway with the highest gene count is missing in the results shown in the paper. From NERI - BAHN - KEGG Analysis: “Pathways of neurodegeneration - multiple diseases”, “Pathways in cancer” - pathways with the highest gene count (30 and 28 respectively) are not mentioned in the paper. Other pathways are present and the paper is somewhat reproducible. | 2 |
| 19. | PMC6526186 |	Table 1 |	1. Yes. 2. Yes. |	The top BP GO terms from the paper are no longer significantly higher in the replicated GO results. The top 2 KEGG Pathways after replication are “Human cytomegalovirus infection” followed by “Pathways in cancer”. The p-values have changed after the results were replicated, compared to the values given in the paper. The rest of the pathways are similar to the results given in the paper. |	2 |
| 20. | PMC6607402 | Figure 1 A-D |	1. Yes. 2. Yes, many! |	For GO analysis and their replication, top enriched BP, CC and MF GO terms are not mentioned. Most of the terms are mentioned in the replicated results, but different levels of enrichment. | 2 |
